Hydras \& Co.

### 2022-02-21 doc/gaia-chapter.tex
add snippets to GCanon.v
Small changes in gaia-chapter; add an ON instance for Mathcomp finite ordinals

Associativity of multiplication over \HydrasLib' type \texttt{T1},
although imported from \gaia, is expressed with \HydrasLib' notations.

\inputsnippets{GaiaToHydra/T1BridgeUseb}

@@

\section{Importing a theorem from \gaia}
The \texttt{Gaia} library already contains many lemmas about
ordinal arithmetic. In this section, we give two examples of
porting such a lemma to \HydrasLib' vocabulary.

@@

The following lemmas are proved by rewriting from corresponding statements proved in \HydrasLib.

\inputsnippets{GCanon/g2hCanonRw}
\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitMono}

>>>>

Section~\ref{sect:gaia2hydra} shows how lemmas on arithmetic properties of ordinals strictly less than $\epsilon_0$ are  imported from \gaia , with \HydrasLib's notations.

@@

\section{Importing a theorem from \gaia}
\label{sect:gaia2hydra}

The \texttt{Gaia} library already contains many lemmas about
ordinal arithmetic. In this section, we give two examples of
porting such a lemma to \HydrasLib' vocabulary.

@@

The following lemmas are proved by rewriting from corresponding statements proved in \HydrasLib.
\inputsnippets{GCanon/g2hCanonRw}

\inputsnippets{GCanon/gcanonZero}
\inputsnippets{GCanon/gcanonSucc}
\inputsnippets{GCanon/gcanonSSn}
\inputsnippets{GCanon/gcanonLim1}
\inputsnippets{GCanon/gcanonLim2}
\inputsnippets{GCanon/gcanonLim3}

\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitMono}
\inputsnippets{GCanon/glimitCanonSNotZero}
